### 2015-09-29 untitled.tex
edited untitled.tex

With the above discussions, for the most simple case defined above, the problem is basically identical to the worst-case response time analysis of segmented self-suspending task systems. It has been recently shown by Nelissen et al. \cite{ecrts15nelissen}  calculating the worst-case response time in the above case is already a very challenging problem. Nelissen et al. \cite{ecrts15nelissen} identify several misconceptions used in the literature for this problem. After excluding those misconceptions, deriving the worst-case response time of a computation segment in pseudo-polynomial time seems to be a very difficult problem. Due to \cite{ecrts15nelissen}, the only existing solution to derive the exact $W_k^{j}$ (and hence $R_k^j$) requires exponential time complexity.

@@

This report explains how to use the period enforcer algorithm proposed by Rajkumar \cite{Raj:suspension1991} to handle segmented self-suspending real-time tasks. One key assumption in the report in \cite{Raj:suspension1991} is that a deferrable task $\tau_i$ can defer its entire execution time but not parts of it. This creates some mismatches between the original sporadic task system and the corresponding deferrable task system.  The report in  \cite{Raj:suspension1991} did not explain how to convert a segmented self-suspending task system to a corresponding deferrable task system. We show in this report that this is non-trivial and the main claim of Theorem 5 in \cite{Raj:suspension1991} does not reflect the schedulability of the original self-suspending task system.

>>>>

With the above discussions, for the most simple case defined above, the problem is basically identical to the worst-case response time analysis of segmented self-suspending task systems. It has been recently shown by Nelissen et al. \cite{ecrts15nelissen}  calculating the worst-case response time in the above case is already a very challenging problem. Nelissen et al. \cite{ecrts15nelissen} identify several misconceptions used in the literature for this problem. After excluding those misconceptions, deriving the worst-case response time of a computation segment in pseudo-polynomial time seems to be a very difficult problem. Due to \cite{ecrts15nelissen}, the only existing solution to derive the exact $W_k^{j}$ (and hence $R_k^j$) requires exponential time complexity. And, also recall the example in \ref{sec:unschedulable}. Even if the conversion is done precisely, the deferrable task system can be more pessimistic than the original self-suspending task system with respect to the schedulability.

@@

This report explains how to use the period enforcer algorithm proposed by Rajkumar \cite{Raj:suspension1991} to handle segmented self-suspending real-time tasks. One key assumption in the report in \cite{Raj:suspension1991} is that a deferrable task $\tau_i$ can defer its entire execution time but not parts of it. This creates some mismatches between the original self-suspending task system and the corresponding deferrable task system.  The report in  \cite{Raj:suspension1991} did not explain how to convert a segmented self-suspending task system to a corresponding deferrable task system. We show in this report that this is non-trivial and the main claim of Theorem 5 in \cite{Raj:suspension1991} does not reflect the schedulability of the original self-suspending task system.
